Political Support in the United States

### 2024-03-16 paper/paper.qmd
Update paper.qmd

Males are less likely to support Biden than Females,
Women most likely to vote for Biden,
Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

@@

>>>>

1.Males are less likely to support Biden than Females,
2.Women most likely to vote for Biden,
3.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

@@

## Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

Based on the analysis of Figure 1 which is located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden. In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races. For example, Black individuals have a total vote of 5293 individuals for Biden, however only 642 individuals support and vote for Trump. This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals.
